Summary Tables

### 2020-02-13 summary_tables_outcomes.Rmd
Move to the right section

@@

### Change in inury per 100K

  if (!city %in% c('buenos_aires', 'mexico_city', 'bogota', 'vizag')){

    for (cs in names(io[[city]]$outcomes$whw)){
      #cs <- 'Baseline'
      #city <- 'accra'
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- left_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T))
      td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

      # print(td4)
    }
    print(kable(el, caption = city))
    cat("\n")
    #kable(print(el), caption = city)
  }

>>>>

### Change in deaths due to injury per 100,000K

  #if (!city %in% c('buenos_aires', 'mexico_city', 'bogota', 'vizag')){

    for (cs in names(io[[city]]$outcomes$whw)){
      # cs <- 'Baseline'
      # city <- 'mexico_city'
      if (length(names(io[[city]]$outcomes$whw$Baseline)) == 2){
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- left_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T))
      td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

      }else if(names(io[[city]]$outcomes$whw$Baseline) == 'whw'){
        td3 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
        td3[td3$mode == 'pedestrian', ]$mode <- 'walking'
      }else {

        td3 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")

      }

      # print(td4)
    }
    print(kable(el, caption = city))
    cat("\n")
    #kable(print(el), caption = city)
  #}

@@
